Thermal reactionomes reveal adaptive responses to thermal extremes in warm

### 2014-10-09 doc/ApTranscriptome_manuscript.Rmd
updated Abstract and Significance Statement

---
title: Thermal reactionomes reveal adaptive responses to thermal extremes in warm
  and cold-climate ant species
author: ' '
csl: ecology.csl
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc_depth: 2
  html_document: null
includes: header.tex
bibliography: ApTranscriptome.bib
---

>>>>

---
title: Thermal reactionomes reveal adaptive responses to thermal extremes in warm
  and cold-climate ant species
author: ' '
csl: ecology.csl
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc_depth: 2
  html_document: null
  word_document: default
includes: header.tex
bibliography: ApTranscriptome.bib
---
